Repeatability Test

### 2017-07-13 pt_characterization/rep_check/u_s_time.tex
July 12 Draft

\section{Further Investigation of the First Run and Some Additional Runs~\label{sec:u_s_time_hist}} 
This section exhibits user and system time histograms on the second run of 
INC with its task length increasing from 1 second to 4096 seconds via EMPv5 with no Step 2.
The detailed description of the base data is from Table~\ref{tab:exp_notes1}, 
and for some additional data, the corresponding description is given in Table~\ref{tab:exp_notes3}.

@@

\begin{figure}[htp!]
\vspace{-.3in}
	\centering
	\includegraphics[scale=0.5,angle=270]{u_s_time/3d_plot.eps}\label{fig:3d_plot}
	\caption{3D histograms on INC~\label{fig:hist3d}}
\end{figure}

@@

\subsection{ET}

%\begin{figure}[hp!]
%	\centering
%	\subfigure[User time frequency on INC3]{
%		\includegraphics[scale=0.43]{u_s_time/3_sec_et_hist.eps}
%		\label{fig:inc3_ut_hist}
%	}
%	\caption{User Time Histograms of INC1 ... INC4~\label{fig:ut_hist1}}
%\end{figure}

\subsection{PT}

%\begin{figure}[hp!]
%	\centering
%	\subfigure[User time frequency on INC3]{
%		\includegraphics[scale=0.43]{u_s_time/3_sec_et_hist.eps}
%		\label{fig:inc3_ut_hist}
%	}
%	\caption{User Time Histograms of INC1 ... INC4~\label{fig:ut_hist1}}
%\end{figure}

>>>>

\section{Further Investigation of the First Run and Some Additional Runs~\label{sec:u_s_time_hist}} 
This section exhibits user and system time histograms on the second run of 
INC with its task length increasing from 1 second to 4096 seconds via EMPv5 with no Step 2.
The detailed description of the base data is from Table~\ref{tab:exp_notes1}, 
and for some additional data, the corresponding description is given in Table~\ref{tab:exp_notes4}.

@@

\begin{figure}[htp!]
\vspace{-.3in}
	\centering
	\includegraphics[scale=0.6,angle=270]{u_s_time/3d_plot.eps}\label{fig:3d_plot}
	\caption{3D histograms on INC~\label{fig:hist3d}}
\end{figure}

@@

\subsubsection{ET}
Not available at this point, due to the labshelf server's unavailability for the time being.

\subsubsection{PT}
The histograms of INC1 through INC4096 are 
the same as those of Figures~\ref{fig:s9_r1_pt_hist1},~\ref{fig:s9_r1_pt_hist2},~\ref{fig:s9_r1_pt_hist3}, and~\ref{fig:s9_r1_pt_hist4}. 
The following are the histograms of INC with some intermediate task lengths.

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC3]{
		\includegraphics[scale=0.43]{u_s_time/3_sec_pt_hist.eps}
		\label{fig:inc3_pt_hist}
	}
	\subfigure[PT frequency on INC6]{
		\includegraphics[scale=0.43]{u_s_time/6_sec_pt_hist.eps}
		\label{fig:inc6_pt_hist}
	}
	\subfigure[PT frequency on INC12]{
		\includegraphics[scale=0.43]{u_s_time/12_sec_pt_hist.eps}
		\label{fig:inc12_pt_hist}
	}
	\subfigure[PT frequency on INC24]{
		\includegraphics[scale=0.43]{u_s_time/24_sec_pt_hist.eps}
		\label{fig:inc24_pt_hist}
	}
	\caption{PT Histograms of INC3 ... INC24~\label{fig:new_pt_hist1}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC48]{
		\includegraphics[scale=0.43]{u_s_time/48_sec_pt_hist.eps}
		\label{fig:inc48_pt_hist}
	}
	\subfigure[PT frequency on INC72]{
		\includegraphics[scale=0.43]{u_s_time/72_sec_pt_hist.eps}
		\label{fig:inc72_pt_hist}
	}
	\subfigure[PT frequency on INC80]{
		\includegraphics[scale=0.43]{u_s_time/80_sec_pt_hist.eps}
		\label{fig:inc80_pt_hist}
	}
	\subfigure[PT frequency on INC88]{
		\includegraphics[scale=0.43]{u_s_time/88_sec_pt_hist.eps}
		\label{fig:inc88_pt_hist}
	}
	\caption{PT Histograms of INC48 ... INC88~\label{fig:new_pt_hist2}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC96]{
		\includegraphics[scale=0.43]{u_s_time/96_sec_pt_hist.eps}
		\label{fig:inc96_pt_hist}
	}
	\subfigure[PT frequency on INC104]{
		\includegraphics[scale=0.43]{u_s_time/104_sec_pt_hist.eps}
		\label{fig:inc104_pt_hist}
	}
	\subfigure[PT frequency on INC112]{
		\includegraphics[scale=0.43]{u_s_time/112_sec_pt_hist.eps}
		\label{fig:inc112_pt_hist}
	}
	\subfigure[PT frequency on INC120]{
		\includegraphics[scale=0.43]{u_s_time/120_sec_pt_hist.eps}
		\label{fig:inc120_pt_hist}
	}
	\caption{PT Histograms of INC96 ... INC120~\label{fig:new_pt_hist3}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC160]{
		\includegraphics[scale=0.43]{u_s_time/160_sec_pt_hist.eps}
		\label{fig:inc160_pt_hist}
	}
	\subfigure[PT frequency on INC192]{
		\includegraphics[scale=0.43]{u_s_time/192_sec_pt_hist.eps}
		\label{fig:inc192_pt_hist}
	}
	\subfigure[PT frequency on INC224]{
		\includegraphics[scale=0.43]{u_s_time/224_sec_pt_hist.eps}
		\label{fig:inc224_pt_hist}
	}
	\caption{PT Histograms of INC169 ... INC224~\label{fig:new_pt_hist4}}
\end{figure}
